Generalized Tractability

### 2023-04-10 GeneralizedTractability_230310.tex
Fred's Home Computer

>>>>

\section{Fred's Attempt at sub-$h$ $T$-Tractability}
May we frame weak tractability more generally?

Let $h:[0,\infty) \to [1,\infty)]$ satisfy
\begin{equation} \label{eq:h_cond}
	h \text{ is non-decreasing}, \qquad 
	h(0)=1, \qquad  [h(x)]^\tau \le h(\tau x) \quad \forall x \ge 0, \tau > 1.
\end{equation}

\begin{definition}
	A problem is sub-$h \circ T$ tractable if
	\begin{equation*}
		\lim_{\varepsilon^{-1} + d \to \infty} \frac{\comp(\varepsilon,d)}{h(cT(\varepsilon^{-1},d,\vp))} = 0 \qquad \forall c>0
	\end{equation*}
\end{definition}

\begin{theorem}\label{thm:subhT}
	The problem is sub-$h \circ T$ tractable if and only if
	\[
	S_{c,\vp}=\sup_{d\in\naturals}  \, \sum_{i=1}^\infty \frac1{h(c\, T(\lambda_{i,d},d,\vp))} <\infty \qquad \forall c > 0.
	\]
\end{theorem}
\begin{proof}
We suppress the $\vp$ dependence, because it does not enter into the proof.

\noindent \textbf{Necessary Condition:}\\
Suppose that the problem is  sub-$h \circ T$ tractable. Then, for any $c>0$ there exists a positive integer $V_c$ such that  
\[
	\comp(\varepsilon,d)\le 
	\left\lfloor{h(cT(\varepsilon^{-1},d)) \right\rfloor \qquad \forall \varepsilon^{-1} + d \ge V_c.
\]
By the definition of complexity in \eqref{eq:comp_def}, it follows that 
\[
	\lambda_{n(\varepsilon,d,c),d} \le \varepsilon \quad \forall \varepsilon^{-1} + d \ge V_c, \qquad \text{where }
	n(\varepsilon,d,c):=\left\lfloor{h(cT(\varepsilon^{-1},d)) \right\rfloor.
\]
Since $h(cT(\cdot,d))$ is non-decreasing, it follows that
\begin{equation*}
		n(\varepsilon,d,c)\le  h(cT(\varepsilon^{-1},d)) \le  h(cT(\lambda^{-1}_{n(\varepsilon,d,c),d},d)) \qquad  \quad \forall \varepsilon^{-1} + d \ge V_c.
\end{equation*}

For a fixed $d$, the largest the largest $\varepsilon$ can be and still satisfy $ \varepsilon^{-1} + d \ge V_c$ is $\max(V_c - d,1)$.   Let 
\begin{equation} \label{eq:nstardef}
	n^*(d,c) : = n(\max(V_c - d,1),d,c) \le h(cT(\max(V_c-d,1),d)
\end{equation} 
By varying $\varepsilon^{-1}$ in the interval $[\max\{1,V_c-d\},\infty)$,  the integer $	n(\varepsilon,d,c)$ attains all values greater than or equal to $n^*(d,c)$.  Thus, 
\begin{align}
		n &\le h(cT(\lambda^{-1}_{n,d},d)) \qquad  \forall n \ge n^*(d,c), \label{eq:subhTneq}\\
		\nonumber
		\frac{1}{h(2 cT(\lambda^{-1}_{n,d},d)) } & \le \frac{1}{[h(cT(\lambda^{-1}_{n,d},d))]^{2}}  \le \frac 1{n^2}   \qquad  \forall n \ge n^*(d,c) \qquad \text{by \eqref{eq:h_cond}}. \\
		\intertext{Combining this inequality with ...}
		\nonumber
		S_{2c} = 	S_{2c,\vp} & =\sup_{d\in\naturals}  \, \sum_{i=1}^\infty \frac1{h(2c\, T(\lambda_{i,d},d))} \\
		\nonumber
		&  = \sup_{d\in\naturals} \left [
		\sum_{i=1}^{n^*(d,c)-1} \frac1{h(2c\, T(\lambda_{i,d},d))}
		+ \sum_{i=n^*(d,c)}^\infty \frac1{h(2c\, T(\lambda_{i,d},d))} 
		\right]\\
		 \nonumber
		 & \le \sup_{d\in\naturals} \left [
\frac{n^*(d,c)-1}{h(2c\, T(\lambda_{\max},d))}
+ \sum_{i=1}^\infty \frac1{n^2}
\right] 
 \qquad \text{by \eqref{eq:subhTneq}}\\ 
		 & \le \sup_{d\in\naturals} \left [
		 \frac{ h(cT(\max(V_c-d,1),d)}{h(2c\, T(\lambda_{\max},d))}
		\right] + \frac{\pi^2}{6}
		\qquad \text{by \eqref{eq:nstardef}.}
\end{align}
	which is equivalent to 
	\[
	\exp(-2c\, (T(\lambda_{n(\varepsilon),d}^{-s},1,\vp) + T(0,d^t,\vp))) \le \frac{1}{(n(\varepsilon)-1)^2}.
	\]
	Therefore,
	\begin{eqnarray*}
		\exp(-2c\, T(0,d^t,\vp)) \sum_{i=1}^\infty \exp(-2c\, T(\lambda_{i,d}^{-s},1,\vp))
		&\le& \exp(-2c\, T(0,d^t,\vp))\, (n^*-1) + \sum_{i=n^*}^\infty \frac{1}{(i-1)^2}\\
		&\le& \exp(-2c\, T(0,d^t,\vp))\, (n^*-1) + \frac{\pi^2}{6}.
	\end{eqnarray*}
	Moreover,
	\begin{eqnarray*}
		\exp(-2c\, T(0,d^t,\vp))\, (n^*-1) &\le & \exp(-2c\, T(0,d^t,\vp))\, 
		\exp (c\, T(V^s,1,\vp) + c\, T(0,d^t,\vp))\\
		&\le & \exp (c\, T(V^s,1,\vp))\\
		&<& \infty,
	\end{eqnarray*}
	independently of $d$. This implies that 
	\[
	\exp(-2c\, T(0,d^t,\vp)) \sum_{i=1}^\infty \exp(-2c\, T(\lambda_{i,d}^{-s},1,\vp))<\infty,
	\]
	also independently of $d$. As $c>0$ was chosen arbitrarily, we can replace $2c$ by $c$ and see
	necessity of the condition in the theorem.

  \textbf{Sufficient Condition:}\\
	We now show sufficiency.
